---
title: "Final Pou4 Revision Code"
output: github_document
---

#### This is supplemental code for additional visualizations and analyses.

###### **Note:** It is compatible with Seurat v.4.0.4.

###### **Revision Strategy:** Seurat objects "oe_epi_suerat" and "wt_epi_cns9_seurat" present in environment generated from "final_pou4_analysis_pipeline.Rmd" were loaded into a new environment, updated and then manipulated by this script. Urls to these objects are provided below.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=TRUE, message = FALSE}
library(Seurat)
library(edgeR)
library(dplyr)
library(Matrix)
library(ggplot2)
```

#### **Update Seurat objects from v2 to v3.**
##### First load objects.
```{r include=TRUE}
oe_epi_seurat_url <- "https://relevant-pou4-data.s3.us-east-2.amazonaws.com/pou4_revision_code_relevant_objects/oe_epi_seurat.rds"
download.file(oe_epi_seurat_url, "oe_epi_seurat.rds")
oe_epi_seurat <- readRDS("oe_epi_seurat.rds")

wt_epi_cns9_seurat_url <- "https://relevant-pou4-data.s3.us-east-2.amazonaws.com/pou4_revision_code_relevant_objects/wt_epi_cns9_seurat.rds"
download.file(wt_epi_cns9_seurat_url, "wt_epi_cns9_seurat.rds")
wt_epi_cns9_seurat <- readRDS("wt_epi_cns9_seurat.rds")
```

```{r include=FALSE}
updated_oe_epi_seurat <- UpdateSeuratObject(oe_epi_seurat)
updated_wt_epi_cns9_seurat <- UpdateSeuratObject(wt_epi_cns9_seurat)
```

#### **Revision 1:** Figure 2c.
###### Perform UMAP on OE Epi Seurat and visualize subclusters.
```{r include=FALSE}
updated_oe_epi_seurat <- RunUMAP(updated_oe_epi_seurat, dims = 1:8)
```

```{r include=TRUE}
UMAPPlot(updated_oe_epi_seurat, reduction = "umap")
```

#### **Revision 2:** Figures S16 and S18.
###### Visualize various quality control metrics in OE Epi and WT Epi and CNS seurats.
```{r include=TRUE}
oe_vln_plot <- VlnPlot(updated_oe_epi_seurat, features = c("nFeature_RNA", "nCount_RNA"), ncol = 2)
oe_scatter_plot <- FeatureScatter(updated_oe_epi_seurat, feature1 = "nCount_RNA", feature2 = "nFeature_RNA")

wt_vln_plot <- VlnPlot(updated_wt_epi_cns9_seurat, features = c("nFeature_RNA", "nCount_RNA"), ncol = 2)
wt_scatter_plot <- FeatureScatter(updated_wt_epi_cns9_seurat, feature1 = "nCount_RNA", feature2 = "nFeature_RNA")

# For OE Epi Clusters.
oe_vln_plot
oe_scatter_plot

# For WT Epi and CNS Clusters.
wt_vln_plot
wt_scatter_plot
```

#### **Revision 3:** Figure S17.
###### Make Log10 Cell Density of UMIs (a) and Number of Genes (b) in OE Epi and WT Epi and CNS Cells
```{r include=TRUE}
# Do for OE Epi.
oe_metadata <- updated_oe_epi_seurat@meta.data
oe_metadata$cells <- rownames(oe_metadata)
oe_metadata$sample <- "OE Epi"
oe_metadata$res.0.5 <- NULL

# Rename columns.
oe_metadata <- oe_metadata %>%
        dplyr::rename(nUMI = nCount_RNA,
                      nGene = nFeature_RNA)

# Do for WT.
wt_metadata <- updated_wt_epi_cns9_seurat@meta.data
wt_metadata$cells <- rownames(wt_metadata)
wt_metadata$sample <- "WT Epi and CNS"
wt_metadata$res.0.6 <- NULL

# Rename columns.
wt_metadata <- wt_metadata %>%
        dplyr::rename(nUMI = nCount_RNA,
                      nGene = nFeature_RNA)

# Combine OE Epi and WT Epi and CNS metadata.
all_meta_data <- rbind(oe_metadata, wt_metadata)
```

#### **Visualize.**
```{r include=TRUE}
all_meta_data %>% 
  	ggplot(aes(color=sample, x=nUMI, fill= sample)) +
  	geom_density(alpha = 0.2) + 
  	scale_x_log10() + 
  	theme_classic() +
  	ylab("log10 Cell Density") +
  	geom_vline(xintercept = 1000) +
    ggtitle("Log10 Cell Density of UMIs in OE Epi and WT Epi and CNS Cells") 

all_meta_data %>% 
  	ggplot(aes(color=sample, x=nGene, fill= sample)) +
  	geom_density(alpha = 0.2) + 
  	scale_x_log10() + 
  	theme_classic() +
  	ylab("log10 Cell Density") +
    ggtitle("Log10 Cell Density of Number of Genes in OE Epi and WT Epi and CNS Cells") 
```


